---
title: "Travel Times around Renaissamce Festival"
output: html_notebook
---

  
```{r,echo=FALSE,warning=FALSE}
library(magrittr)
library(scales)
library(stringr)
library(forecast)
library(leaflet)
library(tidyverse)
library(reshape2)
library(plotly)
library(lubridate)
library(kableExtra)
library(DT)
options(knitr.table.format = "html") 
```

```{r 'setup',include=FALSE}
require(knitr)
opts_knit$set(root.dir = "H:/Projects/11000/11187/TS/Task 2")
```

```{r}

TMC_all <- readxl::read_xlsx("TMC_All.xlsx")
TMC_all <- TMC_all[!is.na(TMC_all$distance),]
str(TMC_all)

```

We combine all of the downloaded trip data for the area from the TTRMS.exe tool.
```{r,warning=FALSE,echo=FALSE}

list_csv <- list.files(pattern = "*.csv")
myfiles <- lapply(list_csv,read.csv)
files <- mapply(cbind,myfiles,'filename' = list_csv,SIMPLIFY = F)
TMC_data <- rbind_list(files)
list_csv
```

The total dimensions of the combined dataset is `r paste(dim(TMC_data)[1],'rows and',dim(TMC_data)[2],'columns')`.

```{r}
head(TMC_data)
```


```{r,echo=FALSE,warning=FALSE}

TMC_data %<>% 
  mutate(Travel.Time..minutes. = as.numeric(Travel.Time..minutes.),
         lubridate =as.POSIXct(TMC_data$Timestamp,format = "%Y-%m-%d %H:%M:%S"))
TMC_data %<>% 
  mutate(hour = as.factor(hour(TMC_data$lubridate)),
         month = as.factor(month(TMC_data$lubridate)),
         year = as.factor(year(TMC_data$lubridate)),
         weekday = factor(weekdays(TMC_data$lubridate),
                          levels = c("Monday","Tuesday",
                                     "Wednesday","Thursday",
                                     "Friday","Saturday","Sunday")),
         day = as.factor(day(TMC_data$lubridate)),
         filename_split = filename) 

TMC_data %<>% 
  separate(filename_split,into = c('Route','Direction','From','NA','To'),sep='_')
TMC_data$To <- sub(".csv",'',TMC_data$To)

TMC_data_merge <- merge(TMC_data,TMC_all[,c('tmc','latitude','longitude')], 
                        by.x = 'From',by.y='tmc',all.x=TRUE)
colnames(TMC_data_merge)[which(names(TMC_data_merge) 
                               %in% c('latitude','longitude'))] <- c('from_latitude','from_longitude')

TMC_data_merge <- merge(TMC_data_merge,TMC_all[,c('tmc','latitude','longitude')], 
                        by.x = 'To',by.y='tmc',all.x=TRUE)
colnames(TMC_data_merge)[which(names(TMC_data_merge) 
                               %in% c('latitude','longitude'))] <- c('to_latitude','to_longitude')


TMC_Unique <- TMC_data_merge[!duplicated(TMC_data_merge$To),
                             c('To','From',"from_latitude","from_longitude",
                               "to_latitude","to_longitude","Direction")]

TMC_GPS1 <- melt(TMC_Unique,measure.vars=c('From'),
                 id.vars=c('from_latitude','from_longitude'),
                 value.name = 'TMC')
TMC_GPS2 <- melt(TMC_Unique,measure.vars=c('To'),
                 id.vars=c('to_latitude','to_longitude'),
                 value.name = 'TMC')

colnames(TMC_GPS1) <- c('Lat','Long','Variable','TMC')
colnames(TMC_GPS2) <- c('Lat','Long','Variable','TMC')
TMC_GPS <- bind_rows(TMC_GPS1,TMC_GPS2)
TMC_GPS$label <- paste(TMC_GPS$Variable,':',TMC_GPS$TMC,sep = '') 
```


```{r,echo=FALSE,fig.height=5}
Traffic_camera <- makeIcon('Traffic_camera.png',iconWidth = 24, iconHeight = 20)

leaflet(data=TMC_GPS,width = '100%') %>%
  setView(lng = -93.550825, lat =  44.721614, zoom = 11)%>%
  addTiles() %>% 
  addMarkers(~Long,~Lat,icon=Traffic_camera,label = ~TMC) %>%
  addProviderTiles(providers$OpenStreetMap)

```



## Introduction <a name="introduction"></a>

We will look at each TMC individually.

## TMCs in Scott County {.tabset .tabset-fade}

### tab 1

#### US-169_Southbound_118N04465_to_118N04464 

```{r,echo=FALSE}
my_plot.decomposed.ts = function(x, title="", ...) {
  xx <- x$x
  if (is.null(xx)) 
    xx <- with(x, if (type == "additive") 
      random + trend + seasonal
      else random * trend * seasonal)
  plot(cbind(observed = xx, trend = x$trend, seasonal = x$seasonal, random = x$random), 
       main=title, ...)
}
```


```{r,echo=FALSE,warnings=FALSE}
dat <- TMC_data_merge %>%
  filter(filename == paste('US-169_Southbound_118N04465_to_118N04464','.csv',sep=''))

dat_GPS1 <- melt(dat[1,],measure.vars=c('From'),
                id.vars=c('from_latitude','from_longitude'),
                value.name = 'TMC')
dat_GPS2 <- melt(dat[1,],measure.vars=c('To'),
                     id.vars=c('to_latitude','to_longitude'),
                     value.name = 'TMC')

colnames(dat_GPS1) <- c('Lat','Long','Variable','TMC')
colnames(dat_GPS2) <- c('Lat','Long','Variable','TMC')
dat_GPS <- bind_rows(dat_GPS1,dat_GPS2)
dat_GPS$label <- paste(dat_GPS$Variable,':',dat_GPS$TMC,sep = '')
```





```{r,echo=FALSE,fig.height=2}
 
leaflet(data=dat_GPS,width = '100%') %>%
  setView(lng = -93.462271, lat =  44.783811, zoom = 11)%>%
  addTiles() %>% 
  addMarkers(~Long,~Lat,icon=Traffic_camera,label = ~TMC) %>%
  addProviderTiles(providers$OpenStreetMap)


```

<pre>



</pre>
```{r,echo=FALSE}
Mean_Travel <- dat[!is.na(dat$Travel.Time..minutes.),] %>% 
  group_by(day=(floor_date(lubridate,"day"))) %>%
  summarise(Mean=mean((Travel.Time..minutes.)),
            Max=max((Travel.Time..minutes.)),
            Min=min((Travel.Time..minutes.)),
            Std=sd((Travel.Time..minutes.)),
            Median=median((Travel.Time..minutes.))) %>%
  arrange(day)
Mean_Travel$year_average <- ma(Mean_Travel$Mean,order=365)
datatable(Mean_Travel,filter = 'top',options = list(pageLength=7))%>% formatRound(colnames(Mean_Travel[,2:7]),3)%>% formatDate(1,method = 'toDateString')
```

```{r,echo=FALSE,fig.height=5,fig.width=10,warning=FALSE}
f <- ggplot(Mean_Travel)+
  geom_line(aes(day,year_average),color='red')+
  geom_line(aes(day,Mean),linetype="dashed",size=.5)+
  #geom_line(aes(day,Median),color='red')+
  scale_x_datetime(breaks = date_breaks("1 month"))+
  scale_y_continuous(expand = c(0,0))+
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
ggplotly(f)


```



We now treat the average travel time per day as a time series. Below is a plot that isolate out the trend and the seasonality of the data set. 



```{r,echo=FALSE}
ts_Time = ts(Mean_Travel$Mean, frequency = 365,start = c(2014))
decompose_Time = decompose(ts_Time, "additive")

#plot(as.ts(decompose_Time$seasonal))
#plot(as.ts(decompose_Time$trend))
#plot(as.ts(decompose_Time$random))
my_plot.decomposed.ts(decompose_Time)
title(main = "US-169_Southbound_118N04465_to_118N04464\n Mean Travel Time Series Analysis")
```


### tab 2

#### CR-42_Westbound_118P05284_to_118P05285

```{r,echo=FALSE,warnings=FALSE}
dat <- TMC_data_merge %>%
  filter(filename == paste('CR-42_Westbound_118P05284_to_118P05285','.csv',sep=''))

dat_GPS1 <- melt(dat[1,],measure.vars=c('From'),
                id.vars=c('from_latitude','from_longitude'),
                value.name = 'TMC')
dat_GPS2 <- melt(dat[1,],measure.vars=c('To'),
                     id.vars=c('to_latitude','to_longitude'),
                     value.name = 'TMC')

colnames(dat_GPS1) <- c('Lat','Long','Variable','TMC')
colnames(dat_GPS2) <- c('Lat','Long','Variable','TMC')
dat_GPS <- bind_rows(dat_GPS1,dat_GPS2)
dat_GPS$label <- paste(dat_GPS$Variable,':',dat_GPS$TMC,sep = '')
```

```{r,echo=FALSE,fig.height=4}
 
leaflet(data=dat_GPS,width = '100%') %>%
  setView(lng = -93.550825, lat =  44.721614, zoom = 11)%>%
  addTiles() %>% 
  addMarkers(~Long,~Lat,icon=Traffic_camera,label = ~TMC) %>%
  addProviderTiles(providers$OpenStreetMap)


```


```{r,echo=FALSE}
Mean_Travel <- dat[!is.na(dat$Travel.Time..minutes.),] %>% 
  group_by(day=(floor_date(lubridate,"day"))) %>%
  summarise(Mean=mean((Travel.Time..minutes.)),
            Max=max((Travel.Time..minutes.)),
            Min=min((Travel.Time..minutes.)),
            Std=sd((Travel.Time..minutes.)),
            Median=median((Travel.Time..minutes.))) %>%
  arrange(day)
Mean_Travel$year_average <- ma(Mean_Travel$Mean,order=365)
datatable(Mean_Travel,filter = 'top',options = list(pageLength=7))%>% formatRound(colnames(Mean_Travel[,2:7]),3)%>% formatDate(1)
```

```{r,echo=FALSE,fig.height=5,fig.width=10,warning=FALSE}
f <- ggplot(Mean_Travel)+
  geom_line(aes(day,year_average),color='red')+
  geom_line(aes(day,Mean),linetype="dashed",size=.5)+
  #geom_line(aes(day,Median),color='red')+
  scale_x_datetime(breaks = date_breaks("1 month"))+
  scale_y_continuous(expand = c(0,0))+
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
ggplotly(f)


```



We now treat the average travel time per day as a time series. Below is a plot that isolate out the trend and the seasonality of the data set. 



```{r,echo=FALSE}
ts_Time = ts(Mean_Travel$Mean, frequency = 365,start = c(2014))
decompose_Time = decompose(ts_Time, "additive")

#plot(as.ts(decompose_Time$seasonal))
#plot(as.ts(decompose_Time$trend))
#plot(as.ts(decompose_Time$random))
my_plot.decomposed.ts(decompose_Time)
title(main = "CR-42_Westbound_118P05284_to_118P05285\n Mean Travel Time Series Analysis")
```

### tab 3

#### US-169_Northbound_118P05065_to_118P05066

```{r,echo=FALSE,warnings=FALSE}
dat <- TMC_data_merge %>%
  filter(filename == paste('US-169_Northbound_118P05065_to_118P05066','.csv',sep=''))

dat_GPS1 <- melt(dat[1,],measure.vars=c('From'),
                id.vars=c('from_latitude','from_longitude'),
                value.name = 'TMC')
dat_GPS2 <- melt(dat[1,],measure.vars=c('To'),
                     id.vars=c('to_latitude','to_longitude'),
                     value.name = 'TMC')

colnames(dat_GPS1) <- c('Lat','Long','Variable','TMC')
colnames(dat_GPS2) <- c('Lat','Long','Variable','TMC')
dat_GPS <- bind_rows(dat_GPS1,dat_GPS2)
dat_GPS$label <- paste(dat_GPS$Variable,':',dat_GPS$TMC,sep = '')
```



```{r,echo=FALSE,fig.height=4}

leaflet(data=dat_GPS,width = '100%') %>%
  setView(lng = -93.671878, lat =  44.658348, zoom = 11)%>%
  addTiles() %>% 
  addMarkers(~Long,~Lat,icon=Traffic_camera,label = ~TMC) %>%
  addProviderTiles(providers$OpenStreetMap)


```



```{r,echo=FALSE}
Mean_Travel <- dat[!is.na(dat$Travel.Time..minutes.),] %>% 
  group_by(day=(floor_date(lubridate,"day"))) %>%
  summarise(Mean=mean((Travel.Time..minutes.)),
            Max=max((Travel.Time..minutes.)),
            Min=min((Travel.Time..minutes.)),
            Std=sd((Travel.Time..minutes.)),
            Median=median((Travel.Time..minutes.))) %>%
  arrange(day)
Mean_Travel$year_average <- ma(Mean_Travel$Mean,order=365)
datatable(Mean_Travel,filter = 'top',options = list(pageLength=7))%>% formatRound(colnames(Mean_Travel[,2:7]),3)%>% formatDate(1)
```



```{r,echo=FALSE,fig.height=5,fig.width=10,warning=FALSE}
f <- ggplot(Mean_Travel)+
  geom_line(aes(day,year_average),color='red')+
  geom_line(aes(day,Mean),linetype="dashed",size=.5)+
  #geom_line(aes(day,Median),color='red')+
  scale_x_datetime(breaks = date_breaks("1 month"))+
  scale_y_continuous(expand = c(0,0))+
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
ggplotly(f)


```



We now treat the average travel time per day as a time series. Below is a plot that isolate out the trend and the seasonality of the data set. 



```{r,echo=FALSE}
ts_Time = ts(Mean_Travel$Mean, frequency = 365,start = c(2014))
decompose_Time = decompose(ts_Time, "additive")

#plot(as.ts(decompose_Time$seasonal))
#plot(as.ts(decompose_Time$trend))
#plot(as.ts(decompose_Time$random))
my_plot.decomposed.ts(decompose_Time)
title(main = "US-169_Northbound_118P05065_to_118P05066\n Mean Travel Time Series Analysis")
```




### tab 4

#### US-169_Southbound_118N05070_to_118N05069

```{r,echo=FALSE}
my_plot.decomposed.ts = function(x, title="", ...) {
  xx <- x$x
  if (is.null(xx)) 
    xx <- with(x, if (type == "additive") 
      random + trend + seasonal
      else random * trend * seasonal)
  plot(cbind(observed = xx, trend = x$trend, seasonal = x$seasonal, random = x$random), 
       main=title, ...)
}
```


```{r,echo=FALSE,warnings=FALSE}
dat <- TMC_data_merge %>%
  filter(filename == paste('US-169_Southbound_118N05070_to_118N05069','.csv',sep=''))

dat_GPS1 <- melt(dat[1,],measure.vars=c('From'),
                id.vars=c('from_latitude','from_longitude'),
                value.name = 'TMC')
dat_GPS2 <- melt(dat[1,],measure.vars=c('To'),
                     id.vars=c('to_latitude','to_longitude'),
                     value.name = 'TMC')

colnames(dat_GPS1) <- c('Lat','Long','Variable','TMC')
colnames(dat_GPS2) <- c('Lat','Long','Variable','TMC')
dat_GPS <- bind_rows(dat_GPS1,dat_GPS2)
dat_GPS$label <- paste(dat_GPS$Variable,':',dat_GPS$TMC,sep = '')
```





```{r,echo=FALSE,fig.height=2}
 
leaflet(data=dat_GPS,width = '100%') %>%
  setView(lng = -93.588347, lat =  44.738049, zoom = 11)%>%
  addTiles() %>% 
  addMarkers(~Long,~Lat,icon=Traffic_camera,label = ~TMC) %>%
  addProviderTiles(providers$OpenStreetMap)


```

<pre>



</pre>
```{r,echo=FALSE}
Mean_Travel <- dat[!is.na(dat$Travel.Time..minutes.),] %>% 
  group_by(day=(floor_date(lubridate,"day"))) %>%
  summarise(Mean=mean((Travel.Time..minutes.)),
            Max=max((Travel.Time..minutes.)),
            Min=min((Travel.Time..minutes.)),
            Std=sd((Travel.Time..minutes.)),
            Median=median((Travel.Time..minutes.))) %>%
  arrange(day)
Mean_Travel$year_average <- ma(Mean_Travel$Mean,order=365)
datatable(Mean_Travel,filter = 'top',options = list(pageLength=7))%>% formatRound(colnames(Mean_Travel[,2:7]),3)%>% formatDate(1,method = 'toDateString')
```

```{r,echo=FALSE,fig.height=5,fig.width=10,warning=FALSE}
f <- ggplot(Mean_Travel)+
  geom_line(aes(day,year_average),color='red')+
  geom_line(aes(day,Mean),linetype="dashed",size=.5)+
  #geom_line(aes(day,Median),color='red')+
  scale_x_datetime(breaks = date_breaks("1 month"))+
  scale_y_continuous(expand = c(0,0))+
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
ggplotly(f)


```



We now treat the average travel time per day as a time series. Below is a plot that isolate out the trend and the seasonality of the data set. 



```{r,echo=FALSE}
ts_Time = ts(Mean_Travel$Mean, frequency = 365,start = c(2014))
decompose_Time = decompose(ts_Time, "additive")

#plot(as.ts(decompose_Time$seasonal))
#plot(as.ts(decompose_Time$trend))
#plot(as.ts(decompose_Time$random))
my_plot.decomposed.ts(decompose_Time)
title(main = "US-169_Southbound_118N05070_to_118N05069\n Mean Travel Time Series Analysis")
```





### tab 5

####US-169_Southbound_118N05071_to_118N05070


```{r,echo=FALSE}
my_plot.decomposed.ts = function(x, title="", ...) {
  xx <- x$x
  if (is.null(xx)) 
    xx <- with(x, if (type == "additive") 
      random + trend + seasonal
      else random * trend * seasonal)
  plot(cbind(observed = xx, trend = x$trend, seasonal = x$seasonal, random = x$random), 
       main=title, ...)
}
```


```{r,echo=FALSE,warnings=FALSE}
dat <- TMC_data_merge %>%
  filter(filename == paste('US-169_Southbound_118N05071_to_118N05070','.csv',sep=''))

dat_GPS1 <- melt(dat[1,],measure.vars=c('From'),
                id.vars=c('from_latitude','from_longitude'),
                value.name = 'TMC')
dat_GPS2 <- melt(dat[1,],measure.vars=c('To'),
                     id.vars=c('to_latitude','to_longitude'),
                     value.name = 'TMC')

colnames(dat_GPS1) <- c('Lat','Long','Variable','TMC')
colnames(dat_GPS2) <- c('Lat','Long','Variable','TMC')
dat_GPS <- bind_rows(dat_GPS1,dat_GPS2)
dat_GPS$label <- paste(dat_GPS$Variable,':',dat_GPS$TMC,sep = '')
```





```{r,echo=FALSE,fig.height=2}
 
leaflet(data=dat_GPS,width = '100%') %>%
  setView(lng = -93.588347, lat =  44.738049, zoom = 11)%>%
  addTiles() %>% 
  addMarkers(~Long,~Lat,icon=Traffic_camera,label = ~TMC) %>%
  addProviderTiles(providers$OpenStreetMap)


```

<pre>



</pre>
```{r,echo=FALSE}
Mean_Travel <- dat[!is.na(dat$Travel.Time..minutes.),] %>% 
  group_by(day=(floor_date(lubridate,"day"))) %>%
  summarise(Mean=mean((Travel.Time..minutes.)),
            Max=max((Travel.Time..minutes.)),
            Min=min((Travel.Time..minutes.)),
            Std=sd((Travel.Time..minutes.)),
            Median=median((Travel.Time..minutes.))) %>%
  arrange(day)
Mean_Travel$year_average <- ma(Mean_Travel$Mean,order=365)
datatable(Mean_Travel,filter = 'top',options = list(pageLength=7))%>% formatRound(colnames(Mean_Travel[,2:7]),3)%>% formatDate(1,method = 'toDateString')
```

```{r,echo=FALSE,fig.height=5,fig.width=10,warning=FALSE}
f <- ggplot(Mean_Travel)+
  geom_line(aes(day,year_average),color='red')+
  geom_line(aes(day,Mean),linetype="dashed",size=.5)+
  #geom_line(aes(day,Median),color='red')+
  scale_x_datetime(breaks = date_breaks("1 month"))+
  scale_y_continuous(expand = c(0,0))+
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
ggplotly(f)


```



We now treat the average travel time per day as a time series. Below is a plot that isolate out the trend and the seasonality of the data set. 



```{r,echo=FALSE}
ts_Time = ts(Mean_Travel$Mean, frequency = 365,start = c(2014))
decompose_Time = decompose(ts_Time, "additive")

#plot(as.ts(decompose_Time$seasonal))
#plot(as.ts(decompose_Time$trend))
#plot(as.ts(decompose_Time$random))
my_plot.decomposed.ts(decompose_Time)
title(main = "US-169_Southbound_118N05071_to_118N05070\n Mean Travel Time Series Analysis")
```





### tab 6

#### MN-13_Northbound_118P05351_to_118P05352

```{r,echo=FALSE}
my_plot.decomposed.ts = function(x, title="", ...) {
  xx <- x$x
  if (is.null(xx)) 
    xx <- with(x, if (type == "additive") 
      random + trend + seasonal
      else random * trend * seasonal)
  plot(cbind(observed = xx, trend = x$trend, seasonal = x$seasonal, random = x$random), 
       main=title, ...)
}
```


```{r,echo=FALSE,warnings=FALSE}
dat <- TMC_data_merge %>%
  filter(filename == paste('MN-13_Northbound_118P05351_to_118P05352','.csv',sep=''))

dat_GPS1 <- melt(dat[1,],measure.vars=c('From'),
                id.vars=c('from_latitude','from_longitude'),
                value.name = 'TMC')
dat_GPS2 <- melt(dat[1,],measure.vars=c('To'),
                     id.vars=c('to_latitude','to_longitude'),
                     value.name = 'TMC')

colnames(dat_GPS1) <- c('Lat','Long','Variable','TMC')
colnames(dat_GPS2) <- c('Lat','Long','Variable','TMC')
dat_GPS <- bind_rows(dat_GPS1,dat_GPS2)
dat_GPS$label <- paste(dat_GPS$Variable,':',dat_GPS$TMC,sep = '')
```





```{r,echo=FALSE,fig.height=2}
 
leaflet(data=dat_GPS,width = '100%') %>%
  setView(lng = -93.588347, lat =  44.738049, zoom = 11)%>%
  addTiles() %>% 
  addMarkers(~Long,~Lat,icon=Traffic_camera,label = ~TMC) %>%
  addProviderTiles(providers$OpenStreetMap)


```

<pre>



</pre>
```{r,echo=FALSE}
Mean_Travel <- dat[!is.na(dat$Travel.Time..minutes.),] %>% 
  group_by(day=(floor_date(lubridate,"day"))) %>%
  summarise(Mean=mean((Travel.Time..minutes.)),
            Max=max((Travel.Time..minutes.)),
            Min=min((Travel.Time..minutes.)),
            Std=sd((Travel.Time..minutes.)),
            Median=median((Travel.Time..minutes.))) %>%
  arrange(day)
Mean_Travel$year_average <- ma(Mean_Travel$Mean,order=365)
datatable(Mean_Travel,filter = 'top',options = list(pageLength=7))%>% formatRound(colnames(Mean_Travel[,2:7]),3)%>% formatDate(1,method = 'toDateString')
```

```{r,echo=FALSE,fig.height=5,fig.width=10,warning=FALSE}
f <- ggplot(Mean_Travel)+
  geom_line(aes(day,year_average),color='red')+
  geom_line(aes(day,Mean),linetype="dashed",size=.5)+
  #geom_line(aes(day,Median),color='red')+
  scale_x_datetime(breaks = date_breaks("1 month"))+
  scale_y_continuous(expand = c(0,0))+
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
ggplotly(f)


```



We now treat the average travel time per day as a time series. Below is a plot that isolate out the trend and the seasonality of the data set. 



```{r,echo=FALSE}
ts_Time = ts(Mean_Travel$Mean, frequency = 365,start = c(2014))
decompose_Time = decompose(ts_Time, "additive")

#plot(as.ts(decompose_Time$seasonal))
#plot(as.ts(decompose_Time$trend))
#plot(as.ts(decompose_Time$random))
my_plot.decomposed.ts(decompose_Time)
title(main = "MN-13_Northbound_118P05351_to_118P05352\n Mean Travel Time Series Analysis")
```





### tab 7

#### MN-41_Southbound_118N05381_to_118N05380

```{r,echo=FALSE}
my_plot.decomposed.ts = function(x, title="", ...) {
  xx <- x$x
  if (is.null(xx)) 
    xx <- with(x, if (type == "additive") 
      random + trend + seasonal
      else random * trend * seasonal)
  plot(cbind(observed = xx, trend = x$trend, seasonal = x$seasonal, random = x$random), 
       main=title, ...)
}
```


```{r,echo=FALSE,warnings=FALSE}
dat <- TMC_data_merge %>%
  filter(filename == paste('MN-41_Southbound_118N05381_to_118N05380','.csv',sep=''))

dat_GPS1 <- melt(dat[1,],measure.vars=c('From'),
                id.vars=c('from_latitude','from_longitude'),
                value.name = 'TMC')
dat_GPS2 <- melt(dat[1,],measure.vars=c('To'),
                     id.vars=c('to_latitude','to_longitude'),
                     value.name = 'TMC')

colnames(dat_GPS1) <- c('Lat','Long','Variable','TMC')
colnames(dat_GPS2) <- c('Lat','Long','Variable','TMC')
dat_GPS <- bind_rows(dat_GPS1,dat_GPS2)
dat_GPS$label <- paste(dat_GPS$Variable,':',dat_GPS$TMC,sep = '')
```





```{r,echo=FALSE,fig.height=2}
 
leaflet(data=dat_GPS,width = '100%') %>%
  setView(lng = -93.588347, lat =  44.738049, zoom = 11)%>%
  addTiles() %>% 
  addMarkers(~Long,~Lat,icon=Traffic_camera,label = ~TMC) %>%
  addProviderTiles(providers$OpenStreetMap)


```

<pre>



</pre>
```{r,echo=FALSE}
Mean_Travel <- dat[!is.na(dat$Travel.Time..minutes.),] %>% 
  group_by(day=(floor_date(lubridate,"day"))) %>%
  summarise(Mean=mean((Travel.Time..minutes.)),
            Max=max((Travel.Time..minutes.)),
            Min=min((Travel.Time..minutes.)),
            Std=sd((Travel.Time..minutes.)),
            Median=median((Travel.Time..minutes.))) %>%
  arrange(day)
Mean_Travel$year_average <- ma(Mean_Travel$Mean,order=365)
datatable(Mean_Travel,filter = 'top',options = list(pageLength=7))%>% formatRound(colnames(Mean_Travel[,2:7]),3)%>% formatDate(1,method = 'toDateString')
```

```{r,echo=FALSE,fig.height=5,fig.width=10,warning=FALSE}
f <- ggplot(Mean_Travel)+
  geom_line(aes(day,year_average),color='red')+
  geom_line(aes(day,Mean),linetype="dashed",size=.5)+
  #geom_line(aes(day,Median),color='red')+
  scale_x_datetime(breaks = date_breaks("1 month"))+
  scale_y_continuous(expand = c(0,0))+
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
ggplotly(f)


```



We now treat the average travel time per day as a time series. Below is a plot that isolate out the trend and the seasonality of the data set. 



```{r,echo=FALSE}
ts_Time = ts(Mean_Travel$Mean, frequency = 365,start = c(2014))
decompose_Time = decompose(ts_Time, "additive")

#plot(as.ts(decompose_Time$seasonal))
#plot(as.ts(decompose_Time$trend))
#plot(as.ts(decompose_Time$random))
my_plot.decomposed.ts(decompose_Time)
title(main = "MN-41_Southbound_118N05381_to_118N05380\n Mean Travel Time Series Analysis")
```










